All praise and gratitude are due to Allah SWT for His abundant grace, blessings, and guidance, which have enabled the author to complete this undergraduate thesis successfully. Throughout the preparation of this thesis, the author received guidance, assistance, and support from many individuals. Therefore, the author would like to express sincere gratitude to:

\begin{enumerate}
	\item Prof. Ir. Hanung Adi Nugroho, S.T., M.Eng., Ph.D., IPM, SMIEEE, Head of the Department of Electrical Engineering and Information Technology, Faculty of Engineering, Universitas Gadjah Mada.

	\item Ir. Lesnanto Multa Putranto, S.T., M.Eng., Ph.D., IPM, Secretary of the Department of Electrical Engineering and Information Technology, Faculty of Engineering, Universitas Gadjah Mada, for facilitating the administrative processes related to the preparation of this thesis.
	
	\item Dr. Iswandi, S.T., M.Eng., Head of the Electrical Engineering Undergraduate Program, for his direction, guidance, and support throughout the author's studies.

	\item Dr. Rian Fatah Mochamad, S.T., M.Eng., the first thesis supervisor, for his guidance, assistance, and direction throughout the completion of this thesis.

	\item Dr. Ir. Mokhammad Isnaeni Bambang Setyonegoro, M.T., the second thesis supervisor, for his valuable suggestions and feedback on this thesis.
	
	\item Mama, Papa, Zifa, and Zira, for their constant prayers, support, and encouragement throughout the author's studies and the completion of this thesis.
	
	\item Tantyaning Embun Pinasthi Wibowo, for her constant companionship, support, and encouragement throughout the author's studies and the completion of this thesis.
	
	\item Mofid, Jally, Tipen, Murguy, Jah, Kims, Arden Este, Daiva, Gesek, Limbultang, Yorick, Aan, Nicho Semir, Atar Semur, Nuel PF, Basit, and other DTETI friends, especially Kelap-kelip, Working Space, and Kaktus, for their support, encouragement, and companionship throughout the author's studies and the completion of this thesis.
\end{enumerate}

Finally, the author hopes that this thesis will be beneficial to all readers.

\begin{flushright}
	\begin{tabular}{c}
		Yogyakarta, June 10, 2026\\
		\vspace{1cm} \\
		Author
	\end{tabular}
\end{flushright}
